Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-06-02 SecDev21/paper.tex
reviewing user's api section

\todo[inline]{KG: fixed up to here}
\section{Hardening the user's API}
\label{sec:API}

A common problem faced by users of the CycloneTCP library is the need to
properly chain calls of the Socket API, in a way that respects the TCP
automaton. This entails verifying that 1)~the functions are called with respect
to a defined order and 2)~the return code is checked before continuing the
processing.

>>>>

\section{Hardening the user's API}
\label{sec:API}

One of the most significant problems pointed to by the primary author of the \emph{CycloneTCP} library is the incorrect usage of the library's API. More specifically, the library's users tend to call the API functions in the wrong order and forget to check the return code of a function call. Thus, they are subsequently allowing their  TCP implementation to behave outside of the functional specification of the protocol. The following sections demonstrate how SPARK can be used to enforce the correct usage of the library.

\todo[inline]{KG: fixed up to here}
